Open-Set Domain Adaptation through Self-Supervision

### 2022-02-12 paper/main.tex
3.6 Performance metrics reviewed

\subsection{Performance Metrics}
\label{sec:performance_metrics}

Evaluating model perfomance requires finding a balance between two values:
{\it OS*}, 
the fraction of correctly classified samples,
and {\it UNK}, 
the fraction of correclty rejected samples.
A model not confident enough to reject a sample could still achieve high {\it OS*} values but near-zero {\it UNK},
while a model rejecting every  sample as unkwnown will achieve perfect {\it UNK} and zero {\it OS*}.
To compare models we use the harmonic mean between {\it OS*} and {\it UNK}, 
defined as $HOS = 2\frac{OS^*\times UNK}{OS^*+UNK}$.
This is because this kind of mean tends gives a bigger weight to the smaller values,
resulting in a more severe evaluation of models.

>>>>

\subsection{Performance metrics}
\label{sec:performance_metrics}

To have a meaningful comparison of the effectiveness
of the models to solve OSDA problems, we need to resort to a metric which
correctly measures the goodness of our predictions.
The difficulty lies on the joint presence of two, usually conflicting, goals.
We recall that an OSDA problem is characterized by the concurrent presence of
a domain difference and a class set difference.
The final goal is to correctly classify the samples belonging to known classes
while rejecting the samples of unknown classes.
The performance of both the goals are typically taken into account by two metrics, {\it OS*},
which is the fraction of the correctly classified samples belonging to known classes, and {\it UNK},
which in contrast is the accuracy over the correctly rejected samples.
Since the goals are usually conflicting, we need an overall metric which is able to correctly balance
the two contributions, providing low values if at least one of the two is low.
We therefore pick the harmonic mean of the two contributions, defined as $HOS = 2\frac{OS^*\times UNK}{OS^*+UNK}$.
We underline that $HOS$ is a more severe and fair metric to effectively measure the goodness of a model to perform well
on a given OSDA problem because, from the definition of the harmonic mean, it tends to give a bigger weight to the smaller values.
